Examining FDR correction issue in clusterProfiler - RNA-seq example

### 2024-09-06 analysis/analyse_rnaseq2.Rmd
investigating gene sets specific to uncorrected annalysis

>>>>

## Investigate which gene sets are specific to the ORIGINAL and FIXED analysis

Will focus on the 500 gene analysis if GO in the seven datasets.

j=1:7

k=gs=6

l=ngenes=500

```{r,deepdive}

compare_ora2 <- function(bad,good){
  badup <- bad$orabad_up
  baddn <- bad$orabad_dn
  goodup <- good$oragood_up
  gooddn <- good$oragood_dn
  bup <- rownames(subset(badup,p.adjust<0.05))
  gup <- rownames(subset(goodup,p.adjust<0.05))
  bdn <- rownames(subset(baddn,p.adjust<0.05))
  gdn <- rownames(subset(gooddn,p.adjust<0.05))
  sig_bad <- unique(c(bup,bdn))
  sig_good <- unique(c(gup,gdn))
  spec_good <- setdiff(sig_good,sig_bad)
  spec_bad <- setdiff(sig_bad,sig_good)
  itx <- intersect(sig_bad,sig_good)
  result=list("spec_bad"=spec_bad,"itx"=itx)
  return(result)
}

ora_dat3 <- mclapply(1:7, function(i) {
  j=params[i,1]
  k=6
  l=500
  bad <- orabad(d[[j]],gs[[k]],l)
  good <- oragood(d[[j]],gs[[k]],l)
  res <- compare_ora2(bad,good)
  return(res)
} , mc.cores=8)

gslengths <- unlist(lapply(gs,function(x) { lapply(x,length) } ) )
names(gslengths) <- sapply((strsplit(names(gslengths),"\\.")),"[[",2)

i=1

spec <- lapply(1:7,function(i) {
  itx_lens <- gslengths[names(gslengths) %in% ora_dat3[[i]][[2]]]
  spec_bad_lens <- gslengths[names(gslengths) %in% ora_dat3[[i]][[1]]]
  if ( length(itx_lens) >= 10 & length(spec_bad_lens) >= 10 ) {
    return(c("spec_bad"=mean(spec_bad_lens),"itx"=mean(itx_lens)))
  } else {
    return(c("spec_bad"=NA,"itx"=NA))
  }
})

spec <- as.data.frame(do.call(rbind,spec))

( spec$spec_bad - spec$itx ) / spec$itx
